Additional analysis

### 2018-04-07 03_additional-analysis.Rmd
Simpler summary

```{r avg-time, results="asis"}
results %>% summarize(min = min(duration),
                      max = max(duration),
                      mean = mean(duration),
                      sd = sd(duration),
                      median = median(duration)) %>% 
  pandoc.table()
```

>>>>

```{r avg-time, results="asis"}
results %>% 
  summarize_at(vars(duration), funs(min, max, mean, sd, median)) %>% 
  pandoc.table()
```
